---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GeoRouteR

<!-- badges: start -->

[![R-CMD-check](https://github.com/STBrinkmann/GeoRouteR/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/STBrinkmann/GeoRouteR/actions/workflows/check-standard.yaml)

<!-- badges: end -->

The goal of GeoRouteR is to provide easy-to-use functions for routing and isochrone analysis on spatial data.

## Installation

You can install the development version of GeoRouteR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("STBrinkmann/GeoRouteR")
```

## Example

### Create a Graph

This is a basic example which shows you how to build a basic S6 Graph object:

```{r example}
library(GeoRouteR)

edges <- data.frame(from = c("A", "A", "C", "B", "A"),
                    to = c("B", "C", "D", "C", "E"),
                    speed = c(10, 20, 40, 100, 20),
                    length = c(1, 2, 2, 1, 3),
                    oneway = c("FT", "B", "N", "TF", "foot_only"))

nodes <- data.frame(node = c("A", "B", "D", "C", "E"),
                    X = c(0, 1, 1, 2, 3),
                    Y = c(0, 0, 1, 1, 2))

crs <- "EPSG:4326"

graph <- makegraph(edges, nodes, crs, directed = TRUE)
graph
```

This code creates a graph with `makegraph()`, using the edge `data.frame` for `from`, `to`, and `cost`, and spatial coordinates from the `nodes` `data.frame` containing the `node`, `X` and `Y` coordinates. The resulting `Graph` object is stored in C++ and a pointer is used for calling the relevant methods.

### Adjust speed profile

You can also change the speed profile to foot, bicylce and car. This will adjust the edge costs and change the graph based on the oneway rules.

-   "foot"\
    Sets speed to 5 km/h, ignores oneway rules and disables roads with speed \> 90 km/h

-   "bicycle"\
    Sets speed to 15 km/h, 4 km/h for foor_only edges, disables roads with speed \> 90 km/h

-   "car"\
    Speed and oneway rules are taken from user input (edges)

-   "default"\
    Restores default settings

```{r}
graph$activate_profile(profile = "foot")
graph
```

```{r}
graph$edges()
```

### Calculate isochrones and distance matrix

We can now use use the `isochrone` function to generate isochrones with the "foot" active.

```{r}
isochrones <- isochrone(graph, from = "A", lim = c(0.02, 0.03))
isochrones
```

We can also use the `distance_matrix` function to calculate the the shortest paths between mutliple nodes in our Graph.

```{r}
dist_mat <- distance_matrix(Graph = graph,
                            from = c("A", "B", "C", "E"),
                            to = c("A", "B", "C", "E"))
dist_mat
```
